\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

% Section formatting
\titlespacing*{\section}{0pt}{\baselineskip}{0.5\baselineskip}
\titlespacing*{\subsection}{0pt}{\baselineskip}{0.25\baselineskip}
\titleformat{\section}{\normalfont\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalfont\large\bfseries}{}{0em}{}

% List formatting
\setlist[itemize]{itemsep=0pt, topsep=0pt}

\begin{document}

\pagestyle{empty}

% Header
\begin{center}
    {\LARGE \textbf{Timofey Krivonosov}}\\
    \vspace{0.2cm}
    \href{mailto:krivonosovTi@gmail.com}{krivonosovTi@gmail.com} \\
    Phone: +7 931 386 9080 \\
    \href{https://github.com/krivonosovti}{GitHub: krivonosovti} \\
\end{center}

\vspace{0.5cm}

% Professional Experience
\section*{Professional Experience}

\textbf{Medika LLC} \hfill September 2022 – Present \\
\textit{IT Specialist} \\

\begin{itemize}
    \item \textbf{Systems Administration and Support:}
    \begin{itemize}
        \item Managed and administered automated workstations (ARM), providing user support and troubleshooting.
        \item Configured and managed VLANs to ensure network security and segmentation.
        \item Administered servers, including performance monitoring, updates, and optimization.
    \end{itemize}

    \item \textbf{Development and Programming:}
    \begin{itemize}
        \item Developed RESTful API applications using Java Spring Boot and PostgreSQL, ensuring robust and scalable solutions.
        \item Utilized database migration frameworks such as Flyway or Liquibase for seamless data transitions.
        \item Created interactive and responsive user interfaces with Vue.js.
        \item Deployed servers on Debian using Docker and Gradle to streamline and automate development processes.
    \end{itemize}

    \item \textbf{Data Analysis and Testing:}
    \begin{itemize}
        \item Applied Python and C++ for data analytics tasks and conducted A/B testing to optimize processes.
        \item Explored stability conditions in dynamic systems, control theory, and mathematical statistics.
    \end{itemize}

    \item \textbf{Competitions and Hackathons:}
    \begin{itemize}
        \item Actively participated in coding contests hosted by Yandex, Tinkoff, and other leading companies, showcasing problem-solving skills.
    \end{itemize}

    \item \textbf{Tools and Technologies:}
    \begin{itemize}
        \item Proficient in version control systems using Git, including branching, merging, and repository management.
        \item Strong understanding and experience with SQL for effective data management and retrieval.
    \end{itemize}
\end{itemize}

\vspace{0.5cm}

% Education
\section*{Education}

\textbf{Saint Petersburg State University} \\
\textit{Major: Applied Mathematics, Computer Science, and AI} \\
Third Year Student (2022 – Present)

\vspace{0.5cm}

% Skills
\section*{Skills}

\begin{itemize}
    \item \textbf{Programming:} Java, Python, C++, JavaScript (Vue.js)
    \item \textbf{Databases:} PostgreSQL, SQL
    \item \textbf{DevOps Tools:} Docker, Gradle
    \item \textbf{System Administration:} Debian, VLAN
    \item \textbf{Development:} RESTful APIs, Spring Boot
    \item \textbf{Analytics:} A/B Testing, Excel, Stability Theory in Dynamic Systems, Lyapunov Stability
    \item \textbf{Machine Learning Libraries}: NumPy, PyTorch, TensorFlow, Matplotlib, Pandas.
        \subitem Not an expert yet, but I have a solid understanding and am continually improving my skills in these libraries.
    \item \textbf{Version Control:} Git
    \item \textbf{Layout}: LaTEX, bibTEX, html.
\end{itemize}

\vspace{0.5cm}

% Personal Qualities
\section*{Personal Qualities}

\begin{itemize}
    \item Diligent and persistent in achieving goals.
    \item Quick learner with enthusiasm for mastering new technologies.
    \item Strong communication skills and team collaboration.
    \item Driver of category "B" with a personal car.
    \item Master of sports in karate.
\end{itemize}

\end{document}
